ms_figures

### 2018-03-20 man/ms_figures.Rmd
change order figure 2

**Figure 2.** EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations. Error bars show standard error.

@@

aes_disturb <- aes(x = disturb_year, y = M.Huber, 
                   color = site, group = site,  
                   fill = site, linetype=site,
                   shape = site, 
                   ymin = lower.ci, ymax = upper.ci)

@@

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free_y"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(
    values=c("N" = 19, "S" = 21, "CA-High"=22, "CA-Low" = 15, "SJ" = 17)), 
  scale_color_manual(
    values=c("N" = 'black',"S" = "blue", "CA-High" = 'blue', "CA-Low" = 'blue', "SJ" = 'black')),
  scale_fill_manual(
    values=c("N" = 'black', "S" = "white", "CA-High" = 'white', "CA-Low" = 'blue', "SJ" = 'black')),
  scale_linetype_manual(values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(
    values=c("N" = 2, "S" = 2, "CA-High"=2.5, "CA-Low" = 2.5, "SJ" = 2.5)),
  geom_text(aes(label=Letter, y=postext), 
            position=pd, 
            show.legend = FALSE, size = 3) 
  # , position_jitterdodge(dodge.width = 0.6, jitter.width = .2)
  # geom_text_repel( 
  #                 nudge_x = - 0.5,
  #                 nudge_y = 0.01,
  #                 direction="both", 
  #                 size = 3.5, show.legend = FALSE,
  #                 segment.size = 0.5, 
  #                 segment.alpha = 0.5) 
)

@@

>>>>

**Figure 2.** EVI standardized anomaly during the period 2000-2016 for northern and southern populations. Error bars show standard error.

@@

aes_disturb <- aes(x = disturb_year, y = M.Huber, 
                   color = site_sorted, group = site_sorted,  
                   fill = site_sorted, linetype=site_sorted,
                   shape = site_sorted, 
                   ymin = lower.ci, ymax = upper.ci)

@@

# orden <- c("N", "S", "SJ", "CA-High","CA-Low")
item_site <- c("0_N" = "N", "1_S" = "S", "2_SJ" = "SJ", "3_CA-High" = "CA-High", "4_CA-Low" = "CA-Low")

themeR <- list(
  geom_errorbar(width=.1, position = pd),
  geom_point(position = pd),
  theme_bw(),
  facet_wrap(~vari, labeller = labeller(vari = variables), scales="free"),
  xlab(''), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    strip.text = element_text(face="bold", size = 14),
    axis.title.y = element_text(face="bold", size = 14),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),
  scale_shape_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 19, "1_S" = 21, "3_CA-High" = 22, "4_CA-Low" = 15, "2_SJ" = 19)), 
  scale_color_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 'black', "1_S" = "blue", "3_CA-High" = 'blue', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_fill_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = 'black', "1_S" = "white", "3_CA-High" = 'white', "4_CA-Low" = 'blue', "2_SJ" = 'black')),
  scale_linetype_manual(labels = item_site, guide = guide_legend(title = NULL),
                        values=c("solid","solid","solid","solid", "solid")),
  scale_size_manual(labels = item_site, guide = guide_legend(title = NULL),
    values=c("0_N" = "2", "1_S" = "2", "3_CA-High" = 2.5, "4_CA-Low" = 2.5, "2_SJ" = 2.5)),

  geom_text(aes(label=Letter, y=postext), 
            position=pd, 
            show.legend = FALSE, size = 3)
  # , position_jitterdodge(dodge.width = 0.6, jitter.width = .2)
  # geom_text_repel( 
  #                 nudge_x = - 0.5,
  #                 nudge_y = 0.01,
  #                 direction="both", 
  #                 size = 3.5, show.legend = FALSE,
  #                 segment.size = 0.5, 
  #                 segment.alpha = 0.5) 
)

@@

m <- m %>% mutate(site_sorted = as.factor(
  case_when(
  site == "N" ~ "0_N",
  site == "S" ~ "1_S",
  site == "SJ" ~ "2_SJ",
  site == "CA-High" ~ "3_CA-High",
  site == "CA-Low" ~ "4_CA-Low"
)))
